draft_final_assignment

### 2022-11-29 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

##Sentiments
```{r}
lex <- get_sentiments("afinn")

text_tokens <- tidy(dfmat) %>% 
  inner_join(lex, by=c("term" = "word"))

doc_sentiments <- tidy(dfmat) %>% 
  inner_join(lex, by=c("term" = "word")) %>% 
  mutate(value=value*count) %>% 
  group_by(document) %>%
  summarise(value = sum(value))

doc_sentiments
```

@@

summary_sentiment <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_w_vader.csv")
```

>>>>

##Sentiments

@@

summary_sentiment <- read_csv("https://raw.githubusercontent.com/juka19/tad_assignment3/main/data/data_w_vader.csv")
```
```{r}
ggplot(summary_sentiment, aes(x = compound)) + 
  geom_histogram(aes(y=..density..), colour="black", fill="white") +
  geom_density(alpha=.1, fill="blue") +
  labs(title="Density of compount sentiment scores",
       x ="Sentiment scores", y = "Density") +
  theme_minimal()
```
